\documentclass[a4paper,11pt]{article}

\usepackage[greek,english]{babel}   % English default; \gr{} for Greek text
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\newcommand{\gr}[1]{\foreignlanguage{greek}{#1}}

\usepackage{amsmath,amssymb,graphicx,booktabs,float,subcaption}
\usepackage{hyperref,listings,xcolor,multirow,array,enumitem}
\usepackage[left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm]{geometry}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breaklines=true, captionpos=b, keepspaces=true,
    numbers=left, numbersep=5pt, tabsize=2
}
\lstset{style=mystyle}

\title{Graph Neural Networks for Predicting Drug Safety Properties\\[0.3em]
\large Mid-Term Progress Report}
\author{
\gr{Κωνσταντίνα Πάσχου} \and
\gr{Γεώργιος Κεσογλίδης} \and
\gr{Θεοχάρης Αγγελίδης}\\[0.4em]
\small Course: Advanced Topics in Machine Learning\\
\small MSc Artificial Intelligence --- Aristotle University of Thessaloniki
}
\date{April 2026}

\begin{document}
\maketitle

\begin{abstract}
This report summarises the work completed so far in our comparative study of
traditional machine learning baselines and Graph Neural Networks (GNNs) for
predicting drug safety properties. Two parallel streams have been developed:
(1) a fingerprint-based baseline using Morgan ECFP4 descriptors with Random Forest
and XGBoost under scaffold-based cross-validation, and (2) a GNN pipeline
evaluating GCN, GIN, GAT, and GraphSAGE on the same benchmark datasets.
Both streams consistently encounter \textbf{class imbalance} as the dominant
challenge. The baseline addresses it with resampling (SMOTE, rejection sampling);
the GNN stream addresses it with class-weighted loss. We report the current state
of both, identify the critical methodological gap between them (different data
splitting strategies), and lay out a concrete plan for the final phase of the
project.
\end{abstract}

\tableofcontents
\newpage

% ─────────────────────────────────────────────────────────────────────────────
\section{Project Context}

Drug development is a long and expensive process, with a large fraction of
candidates failing in clinical trials due to safety concerns. Two key aspects are
\textbf{toxicity} (the drug causes harmful biological effects) and
\textbf{selectivity} (the drug binds to unintended targets, causing side effects).
Predicting these computationally---before synthesis, before animal models---could
significantly reduce cost and time.

Our project, proposed in March 2026, investigates whether \textit{graph-based
molecular representations} offer a measurable advantage over classical
fingerprint-based methods for drug safety prediction. The work is divided between
two complementary streams:

\begin{enumerate}
    \item \textbf{Baseline stream}:
          \begin{itemize}
              \item \gr{Θεοχάρης Αγγελίδης}: AMES benchmark --- naive, classical ML
                    (Morgan FP + RDKit descriptors + RF/XGB), and pre-trained language
                    model (ChemBERTa) under scaffold splits.
              \item \gr{Κωνσταντίνα Πάσχου}: ClinTox and Tox21 under class-imbalance
                    strategies (rejection sampling, SMOTE) with 5-fold CV.
          \end{itemize}
    \item \textbf{GNN stream} --- \gr{Γεώργιος Κεσογλίδης}, \gr{Θεοχάρης Αγγελίδης}:
          four GNN architectures (GCN, GIN, GAT, GraphSAGE) on molecular graphs,
          trained across all 17 toxicity datasets in two experimental phases.
\end{enumerate}

Both streams use datasets from Therapeutics Data Commons (TDC): AMES, hERG\_Karim,
ClinTox, DILI (binary toxicity classification), LD50\_Zhu (acute toxicity
regression), and the 12 Tox21 endpoints. Binding selectivity (DAVIS, KIBA) is the
project's stated stretch goal and is deferred to the final phase.

% ─────────────────────────────────────────────────────────────────────────────
\section{Work Completed}

\subsection{Baseline Stream: Fingerprints + Classical ML + Pre-trained LM}

The baseline stream covers three levels of molecular representation, all evaluated
with \textbf{scaffold-based splits} (Bemis--Murcko scaffolds, same chemical core
always on the same split side) to get a realistic estimate of generalisation to
novel chemical matter.

\subsubsection{Three-Level Hierarchy}

\begin{enumerate}
    \item \textbf{Naive baselines} (floor): majority-class and stratified-random
          classifiers --- establish the minimum meaningful performance.
    \item \textbf{Classical ML + molecular descriptors}: two feature types crossed
          with two classifiers:
          \begin{itemize}
              \item \textit{Morgan fingerprints (ECFP4, 1024-bit, radius 2)}: circular
                    substructure bit vectors, the standard for molecular ML.
              \item \textit{RDKit 2D physicochemical descriptors}: MW, LogP, TPSA,
                    H-bond donors/acceptors --- interpretable but coarser.
          \end{itemize}
          Classifiers: Random Forest (RF, 500 estimators) and XGBoost (500 estimators,
          depth 6).
    \item \textbf{Pre-trained language model}: ChemBERTa (RoBERTa pre-trained on
          77M SMILES) with a frozen backbone and a trainable classification head.
          Represents the current state-of-the-art molecular language model approach.
\end{enumerate}

\subsubsection{Results on AMES (scaffold split)}

AMES is the most balanced dataset ($\approx$50\% positive) and the cleanest
testbed for the fingerprint-vs-graph question. Table~\ref{tab:baseline_ames}
shows results across all three levels.

\begin{table}[H]
\centering
\caption{AMES dataset --- all baseline levels (scaffold split, single train/test).}
\label{tab:baseline_ames}
\begin{tabular}{llrrr}
\toprule
\textbf{Level} & \textbf{Model} & \textbf{ROC-AUC} & \textbf{F1} & \textbf{Accuracy} \\
\midrule
Naive & Dummy (majority)      & ---    & 0.708 & 0.548 \\
Naive & Dummy (stratified)    & 0.517  & 0.557 & 0.520 \\
\midrule
Classical & RF + Morgan FP    & \textbf{0.900} & 0.839 & 0.825 \\
Classical & XGB + Morgan FP   & 0.899  & 0.842 & 0.826 \\
Classical & RF + RDKit desc.  & 0.867  & 0.806 & 0.786 \\
\midrule
Pre-trained LM & ChemBERTa (frozen) & 0.802 & 0.750 & 0.725 \\
\bottomrule
\end{tabular}
\end{table}

Three findings emerge:
\begin{itemize}
    \item \textbf{RF + Morgan FP is the best baseline} (AUROC 0.900). Circular
          substructure fingerprints outperform physicochemical descriptors (0.867)
          and the pre-trained language model (0.802).
    \item \textbf{ChemBERTa underperforms classical ML.} With a frozen backbone,
          ChemBERTa achieves only AUROC 0.802 --- 10 points below RF. SMILES
          embeddings from a language model do not generalise as well as structural
          fingerprints when the backbone is not fine-tuned end-to-end.
    \item \textbf{Fingerprints beat descriptors.} Morgan FP (0.900) outperforms
          RDKit 2D descriptors (0.867), suggesting that local structural topology
          (which substructures are present) is more informative than global
          physicochemical properties for mutagenicity.
\end{itemize}

\subsubsection{Results on ClinTox and Tox21 (class-imbalance regime)}

On heavily imbalanced datasets (\gr{Κωνσταντίνα Πάσχου}'s component), two
strategies were evaluated against the same scaffold splits and 5-fold CV:

\begin{itemize}
    \item \textbf{Cost-Proportionate Rejection Sampling} (under-sampling): custom
          meta-estimator. ClinTox AUROC: 0.794; Tox21 macro-AUROC: 0.744.
    \item \textbf{SMOTE} (over-sampling): Tox21 recall improves to 0.46; ClinTox
          recall remains low (0.20), because the fingerprint space does not separate
          the tiny positive class well enough to generate useful synthetic examples.
\end{itemize}

\textbf{Fingerprints fail entirely on LD50 regression.} LD50 depends on
lipophilicity, polarity, and metabolic stability --- properties a binary bit vector
cannot encode. This is a hard ceiling on the fingerprint approach for regression.

% ─────────────────────────────────────────────────────────────────────────────
\subsection{GNN Stream: Graph Neural Networks}

\subsubsection{From SMILES to Graphs}

Each molecule's SMILES string is parsed by RDKit and converted to a
PyTorch Geometric \texttt{Data} object: a node feature matrix
$\mathbf{X} \in \mathbb{R}^{n_{\text{atoms}} \times F}$ and an edge index encoding
bonds in both directions.

\begin{lstlisting}[language=Python, caption={Per-atom feature extraction.}]
atom_features.append([
    atom.GetAtomicNum(),        # element identity
    atom.GetDegree(),           # bond count
    atom.GetFormalCharge(),     # ionisation state
    int(atom.GetIsAromatic()),  # aromatic ring
    atom.GetTotalNumHs(),       # H-bonding capacity    [added]
    int(atom.IsInRing()),       # ring membership       [added]
    int(atom.GetHybridization()), # local geometry      [added]
    atom.GetTotalValence(),     # total bonding         [added]
    atom.GetNumRadicalElectrons() # radical species     [added]
])
\end{lstlisting}

The four architectures share the same skeleton (two conv layers, global pooling,
linear head) and differ only in their aggregation rule:

\begin{table}[H]
\centering
\caption{GNN architectures.}
\label{tab:models}
\begin{tabular}{lll}
\toprule
\textbf{Model} & \textbf{Aggregation} & \textbf{Key property} \\
\midrule
GCN       & Degree-normalised mean           & Simple, well-understood \\
GIN       & Learnable sum ($\varepsilon$-MLP) & As expressive as 1-WL graph isomorphism test \\
GAT       & Attention-weighted mean (4 heads) & Learns which neighbours matter \\
GraphSAGE & Concatenate self + mean(nbrs)    & Inductive generalisation \\
\bottomrule
\end{tabular}
\end{table}

\subsubsection{Two Training Iterations}

The pipeline was run in two phases to address problems identified in the first.

\begin{table}[H]
\centering
\caption{Configuration changes between phases.}
\label{tab:config}
\begin{tabular}{lll}
\toprule
\textbf{Parameter} & \textbf{Phase 1} & \textbf{Phase 2} \\
\midrule
Atom features      & 4 & 9 (+ ring, H-count, hybridisation, valence, radicals) \\
Hidden dimension   & 16 & 64 \\
Learning rate      & 0.01 & 0.001 \\
Loss (binary)      & BCE, unweighted & BCE + \texttt{pos\_weight = $n_{\text{neg}}/n_{\text{pos}}$} \\
Data split         & Random & Random \\
\bottomrule
\end{tabular}
\end{table}

\subsubsection{Key Results}

\begin{table}[H]
\centering
\caption{GNN stream --- Tox21 macro-AUROC and mean F1 across both phases.}
\label{tab:gnn_results}
\begin{tabular}{lrrrr}
\toprule
 & \multicolumn{2}{c}{\textbf{Phase 1}} & \multicolumn{2}{c}{\textbf{Phase 2}} \\
\cmidrule(lr){2-3}\cmidrule(lr){4-5}
\textbf{Model} & \textbf{Tox21 AUROC} & \textbf{Mean F1} &
                 \textbf{Tox21 AUROC} & \textbf{Mean F1} \\
\midrule
GCN            & 0.705 & 0.108 & 0.732 & 0.279 \\
GIN            & \textbf{0.753} & \textbf{0.307} & \textbf{0.781} & \textbf{0.388} \\
GAT            & 0.721 & 0.122 & 0.748 & 0.314 \\
GraphSAGE      & 0.734 & 0.187 & 0.710 & 0.314 \\
\bottomrule
\end{tabular}
\end{table}

GIN leads in both phases. The class-weighted loss in Phase 2 roughly tripled mean F1
for GCN and GAT (from $\approx$0.11 to $\approx$0.28--0.31), confirming that these
architectures \textit{can} predict the minority class---they just needed the loss
function to demand it. GraphSAGE regressed on three imbalanced datasets after Phase 2
(ClinTox AUROC: 0.804 $\rightarrow$ 0.534), suggesting its aggregation is more
sensitive to aggressive loss reweighting.

% ─────────────────────────────────────────────────────────────────────────────
\section{What We Can and Cannot Compare Yet}

The two streams cannot be directly compared in their current form due to a critical
methodological difference:

\begin{table}[H]
\centering
\caption{Methodological gap between the two streams.}
\label{tab:gap}
\begin{tabular}{lll}
\toprule
 & \textbf{Baseline stream} & \textbf{GNN stream} \\
\midrule
Data split        & Scaffold split (rigorous) & Random split (optimistic) \\
Imbalance method  & Resampling (data-side)    & Weighted loss (model-side) \\
Validation        & 5-fold cross-validation   & Single train/val/test split \\
LD50 regression   & Fails                     & $R^2 = 0.49$ (GIN, Phase 2) \\
\bottomrule
\end{tabular}
\end{table}

\noindent Random splits over-estimate generalisation because structurally similar
molecules leak between train and test. The GNN's Tox21 AUROC of 0.781 is not
directly comparable to the baseline's 0.744 until both use the same scaffold splits.

The gap that \textit{is} already meaningful: the GNN stream produces a working LD50
regression ($R^2 = 0.49$) while the fingerprint baseline fails entirely. Molecular
graphs carry geometric and valence information that binary bit vectors cannot encode.

% ─────────────────────────────────────────────────────────────────────────────
\section{Shared Observations Across Both Streams}

Despite the methodological gap, both streams converge on the same core problem:

\paragraph{Class imbalance is the dominant challenge.}
Positive ratios of 4--14\% across Tox21 endpoints, 8\% for ClinTox. Every technique
we applied was a response to this: rejection sampling, SMOTE, threshold calibration,
class-weighted loss. The fingerprint stream found that SMOTE helps (Tox21 recall
$+$20\%) but is insufficient for ClinTox (recall 0.20 even after over-sampling)
because the fingerprint space does not separate the two classes well enough to
generate useful synthetic examples. The GNN stream found that in-training reweighting
is more effective than post-hoc threshold adjustment.

\paragraph{ClinTox is hard for fundamentally different reasons.}
The baseline achieves ROC-AUC 0.794 with scaffold splits + rejection sampling.
The GNN achieves ROC-AUC 0.812 but only with random splits (0.922 Phase 1, 0.812
Phase 2). Even with 8\% class imbalance, the underlying chemical signal is
weak---molecules that failed clinical trials due to toxicity are not structurally
separable from approved drugs by either representation.

% ─────────────────────────────────────────────────────────────────────────────
\section{Next Steps}

The following items form the plan for the final phase of the project, ordered by
priority and logical dependency.

\subsection{Step 1 --- Align Data Splits (Critical)}

\textit{This must happen before any other comparison is meaningful.}

Switch the GNN pipeline to scaffold-based splitting:

\begin{lstlisting}[language=Python, caption={Scaffold split via TDC.}]
split = Tox(name='AMES', path=DATA_PATH).get_split(
    method='scaffold', seed=42, frac=[0.7, 0.1, 0.2]
)
\end{lstlisting}

Both streams will then operate on the same splits and the headline comparison ---
\textit{fingerprint + XGBoost vs. GNN on structurally novel molecules} --- will be
valid. Expected: GNN AUROC numbers will drop by 0.05--0.15 relative to current
random-split results.

\subsection{Step 2 --- Direct Comparison on Equal Footing}

Once scaffold splits are in place, run both streams on the same datasets and report
a unified results table:

\begin{table}[H]
\centering
\caption{Planned unified comparison table. Baseline numbers confirmed;
         GNN scaffold-split numbers to be filled after Step 1.}
\label{tab:planned}
\begin{tabular}{lrrrr}
\toprule
\textbf{Dataset} & \textbf{Best baseline} & \textbf{Baseline AUROC} &
                   \textbf{Best GNN (random)} & \textbf{GNN (scaffold, TBD)} \\
\midrule
AMES       & RF + Morgan FP  & \textbf{0.900} & GIN 0.851 & --- \\
hERG\_Karim & ---            & ---             & GIN 0.849 & --- \\
ClinTox    & XGB + rej.\ samp. & 0.794        & GIN 0.812$^\dagger$ & --- \\
DILI       & ---             & ---             & GAT 0.877 & --- \\
Tox21 (macro) & XGB + rej.\ samp. & 0.744    & GIN 0.781$^\dagger$ & --- \\
\bottomrule
\multicolumn{5}{l}{$^\dagger$ Random split; not directly comparable to scaffold-split baseline.}
\end{tabular}
\end{table}

This table is the central deliverable of the final report.

\subsection{Step 3 --- Fix GraphSAGE Regression}

GraphSAGE regressed on three imbalanced datasets after Phase 2 due to aggressive
\texttt{pos\_weight}. Two candidate fixes:

\begin{itemize}
    \item \textbf{Cap pos\_weight}: \texttt{pw = min(n\_neg/n\_pos, 10)} --- simple
          and controllable.
    \item \textbf{Focal loss}: $(1 - p_t)^\gamma \cdot \text{BCE}$ with
          $\gamma \in \{1, 2\}$ --- down-weights easy examples rather than
          up-weighting hard ones; more principled.
\end{itemize}

Run as Phase 3 overnight after scaffold splits are in place.

\subsection{Step 4 --- Bond Features as Edge Attributes}

Currently the GNN knows \textit{which} atoms are connected but not \textit{how}.
Adding bond features closes the most significant remaining information gap:

\begin{lstlisting}[language=Python, caption={Bond feature extraction.}]
for bond in mol.GetBonds():
    bond_features.append([
        bond.GetBondTypeAsDouble(),   # 1.0 / 1.5 / 2.0 / 3.0
        int(bond.GetIsConjugated()),
        int(bond.IsInRing()),
        int(bond.GetStereo() != Chem.BondStereo.STEREONONE),
    ])
data.edge_attr = torch.tensor(bond_features, dtype=torch.float)
\end{lstlisting}

Requires swapping \texttt{GINConv} $\rightarrow$ \texttt{GINEConv} for GIN, and
adding \texttt{edge\_dim=4} to \texttt{GATConv}. Expected gain: LD50 $R^2$
$\rightarrow$ 0.55--0.60; modest improvement on Tox21 endpoints.

\subsection{Step 5 --- Multi-Task Tox21}

Currently, 12 separate models are trained on 12 Tox21 endpoints. The endpoints share
the same molecules and are biologically correlated (NR-AR and NR-AR-LBD test the
same receptor). Training a single GNN with 12 output heads and a masked loss
exploits these correlations:

\begin{lstlisting}[language=Python, caption={Masked multi-task BCE loss.}]
# mask = 1 where assay result exists, 0 for missing data
loss = (mask * F.binary_cross_entropy_with_logits(
    logits, targets, reduction='none')).sum() / mask.sum()
\end{lstlisting}

Expected: $+$0.02--0.05 macro-AUROC, $4\times$ fewer trained models.
Estimated effort: 1 day.

\subsection{Step 6 --- Binding Selectivity: DAVIS / KIBA}

The proposal's second objective. Predicting binding affinity requires a joint model:
drug graph $+$ protein sequence $\rightarrow$ binding score. Architecture:

\begin{enumerate}
    \item \textbf{Drug encoder}: GIN backbone from Phase 2 (best-performing).
    \item \textbf{Protein encoder}: pretrained ESM-2 embeddings (1280-dim per
          protein, Meta AI). This is the current state of the art for protein
          representation.
    \item \textbf{Joint head}: concatenate drug and protein embeddings $\rightarrow$
          MLP $\rightarrow$ scalar (Kd or KIBA score).
    \item \textbf{Loss}: MSE on log-scale affinity.
\end{enumerate}

Expected: DAVIS $R^2 \in [0.65, 0.75]$, comparable to recent published GIN+ESM-2
baselines. Estimated effort: 1 week.

\subsection{Step 7 --- Interpretability}

Both streams should be asked: \textit{which structural features drive predictions?}
\begin{itemize}
    \item \textbf{GNN}: GNNExplainer~\cite{ying2019gnnexplainer} identifies the
          minimal subgraph that preserves each prediction. Cross-reference with known
          toxicophores (nitroaromatics, alkyl halides, Michael acceptors).
    \item \textbf{Baseline}: SHAP values on XGBoost identify which fingerprint bits
          are most predictive per endpoint.
\end{itemize}

Comparing the two would reveal whether GNNs and fingerprints exploit the same
structural patterns---or whether GNNs find something fingerprints miss.

% ─────────────────────────────────────────────────────────────────────────────
\section{Summary Timeline}

\begin{table}[H]
\centering
\caption{Final phase plan.}
\label{tab:timeline}
\begin{tabular}{clll}
\toprule
\textbf{Step} & \textbf{Task} & \textbf{Owner} & \textbf{Est. time} \\
\midrule
1 & Scaffold splits for GNN pipeline   & \gr{Γεώργιος}, \gr{Θεοχάρης} & 0.5 day + overnight \\
2 & Unified comparison table            & All & 1 day analysis \\
3 & Fix GraphSAGE (focal loss / cap)   & \gr{Γεώργιος} & 0.5 day + overnight \\
4 & Bond features                       & \gr{Θεοχάρης} & 1--2 days \\
5 & Multi-task Tox21                    & \gr{Γεώργιος} & 1 day \\
6 & DAVIS / KIBA DTI pipeline           & All & 1 week \\
7 & Interpretability (GNNExplainer + SHAP) & All & 2--3 days \\
\midrule
  & Final report writing \& figures    & All & 1 week \\
\bottomrule
\end{tabular}
\end{table}

% ─────────────────────────────────────────────────────────────────────────────
\section{Conclusion}

Both streams are operational and producing results. The central finding shared
across both is that \textbf{class imbalance}, not model capacity, is the dominant
limiting factor on most toxicity datasets. The two streams address it differently:
data-side resampling (baseline) vs. model-side loss reweighting (GNN). Whether one
approach is systematically better than the other is the key remaining question, and
it cannot be answered until Step 1 (scaffold splits) is complete.

The GNN stream's most distinctive advantage is already visible in Phase 2: a working
LD50 regression ($R^2 = 0.49$) that the fingerprint approach cannot produce at all.
This is the clearest evidence so far that graph representations carry information
that binary fingerprints discard.

% ─────────────────────────────────────────────────────────────────────────────
\appendix

\section{Reproducibility}
\begin{itemize}
    \item \texttt{notebooks/data\_exploration.ipynb} --- GNN pipeline
    \item \texttt{models/v1/}, \texttt{models/v2/} --- saved GNN weights
    \item \texttt{results/v1/}, \texttt{results/v2/} --- GNN metrics (CSV)
    \item \texttt{plots/}, \texttt{plots/v2/} --- all generated figures
    \item \texttt{docs/experiment\_progression.md} --- change log
\end{itemize}

\section{Software Stack}
\begin{itemize}
    \item Python 3.12, PyTorch (ROCm 7.2), PyTorch Geometric --- GNN pipeline
    \item scikit-learn, XGBoost --- baseline pipeline
    \item RDKit --- SMILES parsing, fingerprints, atom features
    \item Therapeutics Data Commons (TDC) --- datasets and scaffold splits
    \item pandas, matplotlib, TensorBoard --- analysis and monitoring
\end{itemize}

\begin{thebibliography}{9}

\bibitem{xu2019powerful}
K.~Xu, W.~Hu, J.~Leskovec, and S.~Jegelka,
``How powerful are graph neural networks?,'' \textit{ICLR}, 2019.

\bibitem{kipf2017semi}
T.~N. Kipf and M.~Welling,
``Semi-supervised classification with graph convolutional networks,''
\textit{ICLR}, 2017.

\bibitem{velickovic2018graph}
P.~Veli{\v{c}}kovi{\'c} et al.,
``Graph attention networks,'' \textit{ICLR}, 2018.

\bibitem{hamilton2017inductive}
W.~Hamilton, Z.~Ying, and J.~Leskovec,
``Inductive representation learning on large graphs,'' \textit{NeurIPS}, 2017.

\bibitem{ying2019gnnexplainer}
Z.~Ying et al.,
``GNNExplainer: Generating explanations for graph neural networks,''
\textit{NeurIPS}, 2019.

\bibitem{huang2021therapeutics}
K.~Huang et al.,
``Therapeutics Data Commons,''
\textit{NeurIPS Datasets and Benchmarks}, 2021.

\end{thebibliography}

\end{document}
